Unsupervised embeddings of organizations capture latent structure of scientific mobility

### 2020-03-31 paper/current/main.tex
Update figure 6 and related text

In addition to encoding national characteristics, the embedding also encodes domestic geography and latent hierarchy.
We employ SemAxis~\autocite{an2018semaxis}, a tool utilizing the unique vector arithmetic of semantic embeddings, to project U.S. universities onto two defined axes.
The first axis is geographic, defined using the mean vector of universities in California on one end, and Massachusetts on the other.
The second axis relates instead to prestige.
Universities hiring and mobility networks are known to exhbit latent pretige hierarchies ~\autocite{deville2014career, clauset2015hierarchy} that should be encoded in the embedding space.
The elite end of the axis is defined as the top 20 U.S. universities according to the Times Ranking of World Universities, whereas the non-elite axis is defined as bottom-ranked geographically matched (by U.S. census region) set of universities.
A university projected onto the axis corresponds to their nearness to the mean vector defining each pole.
With a few exceptions, all universities in California are nearer the appropriate end of the axis than are Massachusetts universities, and \textit{vice versa} (Fig.~\ref{fig:semaxis}).
Universities in bordering states, such as Arizona and Connecticut, are closer to the ends of the axis (Fig.~\ref{fig:supp:semaxis_states}b and Fig.~\ref{fig:supp:semaxis_states}e).
Universities in new York are nearer to the Massachusetts end of the axis (Fig.~\ref{fig:supp:semaxis_states}f), whereas universities in Florida are less aligned to either (Fig.~\ref{fig:supp:semaxis_states}i).

Prestigious universities, such as Stanford, Colombia, MIT, Harvard, and NYU, group towards the top of the axis.
Universities at the bottom of this axis tend to be regional universities with lower national profiles, such as California State University Long Beach, University of West Florida, and Barry University.
There are strong differences by state in terms of prestige---overall, universities in Massachusetts are nearer the \textit{Elite} end of the axis than are universities in Arizona, Connecticut, Pennsylvania, and Florida (Fig.~\ref{fig:supp:semaxis_states}).

Once these axes are constructed using university rankings, we can even relate other types of organizations that wouldn't typically be fit onto university rankings.
For example, among Government institutions, we see that the U.S. Department of Energy is more aligned with Californian universities, whereas the Mayo Clinic is more aligned with Massachusetts and organizations like the National Institute of Arthritis, Musculoskeletal, and Skin Disease and more aligned with elite universities than is the U.S. Department of Agriculture (Fig.~\ref{fig:supp:semaxis_sectors}a).
Among research institutes, the most aligned with elite universities are typically those prestigious university-adjacent institutes such as the Whitehead Institute, the Broad Institute, and the Dana Faber institute (Fig.~\ref{fig:supp:semaxis_sectors}b); those institutes aligned with lowly-ranked universities tend to be ecological or agricultural institutes such as the Joseph W. Jones Ecological Research Center and the Louisiana Agriculture Center.
Among teaching organizations, the top-ranked tend to be notable private liberal arts colleges such as Wellesley College and Carleton College, whereas community colleges and military colleges tend to be more aligned with lowly-ranked universities (Fig.~\ref{fig:supp:semaxis_sectors}c).

>>>>

The results demonstrating embeddings' ability to capture various features governing mobility raise the question of whether they can also capture semantic axes analogously to word embeddings. 
For instance, does the mobility embedding encode information about the prestige or universities?
In addition to encoding national characteristics, the embedding also encodes domestic geography and latent hierarchy.
Employing the SemAxis approach~\autocite{an2018semaxis} we define two axes.
The first is the California--Massachusetts axis defined by the mean vector of universities in California on one end, and in Massachusetts on the other. 
The second axis is the low- to high- prestige axis;
the elite end of the axis is defined as the top 20 U.S. universities according to the Times Ranking of World Universities, whereas the non-elite axis is defined as bottom-ranked and geographically matched (by U.S. census region) set of universities.
A university projected onto the axis corresponds to their nearness to the mean vector defining each pole (Fig.~\ref{fig:semaxis}a).
Generally, universities in Western states, such as Arizona (Fig.~\ref{fig:supp:semaxis_states}b) are nearer to the California end of the axis, whereas states in the Northeast such as New York (Fig.~\ref{fig:supp:semaxis_states}f) and Connecticut (Fig.~\ref{fig:supp:semaxis_states}e) are nearer the Massachusetts end.
Universities geographically distance from both California and Massahcussets are less aligned with either, such as Texas (Fig.~\ref{fig:supp:semaxis_states}g)s and Florida (Fig.~\ref{fig:supp:semaxis_states}i).

Universities hiring and mobility networks are known to exhbit latent pretige hierarchies ~\autocite{deville2014career, clauset2015hierarchy} that should be encoded in the embedding space.
Accordingly, prestigious universities such as Stanford, Colombia, MIT, Harvard, and NYU, group towards the top of the axis.
Universities at the bottom of this axis tend to be regional universities with lower national profiles.

Once these axes are constructed using university rankings, we can even relate other types of organizations that would not typically be fit onto university rankings.
For example, among Government institutions, we see that the U.S. Department of Energy is more aligned with Californian universities, whereas the Mayo Clinic is more aligned with Massachusetts and organizations like the National Institute of Arthritis, Musculoskeletal, and Skin Disease and more aligned with elite universities than is the U.S. Department of Agriculture (Fig.~\ref{fig:supp:semaxis_sectors}a).
Among research institutes, the most aligned with elite universities are typically those prestigious university-adjacent institutes such as the Whitehead Institute, the Broad Institute, and the Dana Faber institute (Fig.~\ref{fig:supp:semaxis_sectors}b); those institutes aligned with low-ranked universities tend to be ecological or agricultural institutes such as the Joseph W. Jones Ecological Research Center and the Louisiana Agriculture Center.
Among teaching organizations, the top-ranked tend to be notable private liberal arts colleges such as Wellesley College and Carleton College, whereas community colleges and military colleges tend to be more aligned with low-ranked universities (Fig.~\ref{fig:supp:semaxis_sectors}c).
